\documentclass[12pt]{article}

% Packages
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{comment} % enables the use of multi-line comments (\ifx \fi) 
\usepackage{booktabs, caption, fixltx2e}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{lscape}
\usepackage{pdflscape}
\usepackage[bottom]{footmisc}
\usepackage{ulem}
\usepackage[mdpgd-garamond]{mathdesign}
\usepackage{fontawesome}
\parskip=0pt plus 1pt % spaces betewn paragrpah

% References
\usepackage{xcolor}
\definecolor{darkslateblue}{rgb}{0.28, 0.24, 0.55}
\usepackage{hyperref} 
\hypersetup{backref=true,       
    pagebackref=true,               
    hyperindex=true,                
    colorlinks=true,                
    breaklinks=true,                
    urlcolor= blue,                
    linkcolor= blue,                
    bookmarks=true,                 
    bookmarksopen=false,
    filecolor=darkslateblue,
    citecolor=darkslateblue,
    linkbordercolor=darkslateblue
}

% Settings
\usepackage{geometry}
\geometry{letterpaper, top=20mm,bottom=20mm, left=20mm, right=20mm}
\renewcommand{\baselinestretch}{1.1} % Interlineado
\setlength{\parindent}{0cm} % Sangria 0
\usepackage{blindtext}
\usepackage{fancyhdr} % Style
\pagestyle{fancy} % Style
\fancyfoot[R]{\fontsize{9pt}{9pt}\selectfont\thepage} % Set the right side the page number
\renewcommand{\headrulewidth}{0pt} % Clear the header and footer
\fancyhf{}  % Clear the header and footer

% Tables caption 
\usepackage{threeparttable}
\usepackage{longtable} % tablas en mas de una pagina
\usepackage{multicol}
\captionsetup[table]{labelfont=bf, labelsep=newline}

% Defines columns for tables
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

% lineas horizontales
%\usepackage{ragged2e}
%\usepackage[margin=0.5in]{geometry}
\setlength{\parindent}{0cm}
\usepackage{setspace}

\begin{document}
%---- TITEL ----%
\begin{center}
\par{\huge \textbf{Eduard Fernando Martínez González}\par}
 Department of Economics, Universidad de los Andes, Bogotá, Colombia. \\
\faEnvelope \hspace{0.05cm} \href{mailto:ef.martinezg@uniandes.edu.co}{ef.martinezg@uniandes.edu.co} \faGlobe \hspace{0.05cm} \href{https://eduard-martinez.github.io/}{personal website} \faGithub \hspace{0.05cm} \href{https://github.com/eduard-martinez}{github}
\end{center}

%---- Current Position  ----%
\subsubsection*{Current Position}
\vspace{-20pt}
\rule{\textwidth}{1pt} \hfill
\begin{tabular}{r|p{15cm}}
     & \textbf{Superintendencia de Economía Solidaria.} \\
2023 - & Director of the Data Analytics Group. \\
     & \textbf{Departament of Economics, Universidad de los Andes.} \\
2019 - & Adjunct professor: Statistical \& R Programming  Workshop Seminar.
\end{tabular} 

%---- Education  ----%
\subsubsection*{Education}
\vspace{-20pt}
\rule{\textwidth}{1pt} \hfill
\begin{tabular}{r|p{15cm}}
         & \textbf{Departament of Economics, Universidad de los Andes, Colombia.} \\
2024 & PhD. in Economics. \\

2022 & M.Sc in Economics. \\
\multicolumn{2}{c}{} \\
         & \textbf{Departament of Economics, Universidad del Magdalena, Colombia.} \\
2017 & B.A. In Economics.
\end{tabular} 

%---- Research Interests ----%
\subsubsection*{Research Interests}
\vspace{-20pt}
\rule{\textwidth}{1pt} 
Applied Econometrics, Big Data and Machine Learning, Public Policy, Illegal Markets.

%---- Working Papers ----%
\subsubsection*{Working Papers}
\vspace{-20pt}
\rule{\textwidth}{1pt} 

Coca-Based Local Growth and Its Socio-Economic Impact in Colombia. [\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4931812}{PDF}] (with \href{https://scholar.google.com/citations?user=eKUIyD0AAAAJ&hl=es}{Lucas Marín Llanes}, \href{https://man-fern.github.io/}{Manuel Fernández}, \href{https://sites.google.com/view/maria-alejandra-velez}{María Alejandra Vélez} and Paulo Murillo) \\

The Role of Land Titling and Market Access in the Reduction of Illicit Crops. [\href{https://www.dropbox.com/scl/fi/n66jbiiohquozfkk38ncc/fxs_crops.pdf?rlkey=c4s740k1zb1uw17zp3xa254ra&dl=0}{PDF}] (With \href{https://sites.google.com/site/marialopezuribe00/}{María del Pilar López-Uribe} and \href{https://www.eafit.edu.co/docentes-investigadores/Paginas/juan-carlos-munoz.aspx}{Juan Carlos Muñoz-Mora}) \\

The Role of Big Data in Compliance: Evidence from Randomized Controlled Trials in Colombia. (With \href{https://sites.google.com/site/cesarmantila/}{Cesar Mantilla} and Angel Castillo) \\

Payroll Taxes, Wage Rigidities and Youth Unemployment: Evidence from Colombian Labor Market. [\href{https://danilo-aristizabal.github.io/research/youth_unemployment/taxes_and_youth_unemployment.pdf}{PDF}] (With \href{https://danilo-aristizabal.github.io/}{Danilo E. Aristizabal-Giraldo}). \\

Restrictions on Urban Mobility and Crime: Evidence from Motorcycle Bans in Colombia. [\href{https://www.dropbox.com/scl/fi/ypymvh8iys7p37w26fcpv/motorcycle_restrictions_and_crime.pdf?rlkey=72pll0udfipit53jgaeib7jfd&st=zelhrw52&dl=0}{PDF}] (With \href{http://michael-weintraub.squarespace.com}{Michael Weintraub} and \href{https://investiga.banrep.gov.co/es/profile/76}{Leonardo Bonilla-Mejía}) \\

Losing the Lottery: Household Financial Shocks and Crime. [\href{https://www.dropbox.com/scl/fi/mwacog7h34uu3vfjf7yl8/capitulo_1.pdf?rlkey=83i5sndjm3rprkl2285spv6l9&dl=0}{PDF}]. \\

%---- Publications ----%
\subsubsection*{Publications}
\vspace{-20pt}
\rule{\textwidth}{1pt}

Bonilla-Mejía, L. y Martínez-González, E., (2017). Educación Escolar para la Inclusión y la Transformación Social en el Caribe Colombiano. \textit{Revista del Banco de la República}, \textit{90(1080), 13–45}. \\

Bayona-Velásquez, Etna M.; Erazo-Ortiz, Dayanna S. y Martínez-González, Eduard F. (2018). Fomento a la innovación en la industria manufacturera de Colombia: Un análisis cuantitativo para 2013-2014. \textit{Dimensión Empresarial}, \textit{17(1), 15-28}.

%---- Research Employment ----%
\subsubsection*{Research Employment}
\vspace{-20pt}
\rule{\textwidth}{1pt} \hfill \\
\begin{tabular}{r|p{15cm}}
     & \textbf{International Fund for Agricultural Development (IFAD)} \\
2022 - 2023  & Consultant – Economist at Research and Impact Assessment (RIA).\\
 & With Sara Savastano and Aslihan Arslan. \\
\multicolumn{2}{c}{} \\
   & \textbf{School of Finance, Economy and Government, Universidad EAFIT, Colombia.} \\
2021 & Research Analyst at Centro de Investigaciones Económicas y Financieras (CIEF).\\
     & Prof. Santiago Tobón. \\
\multicolumn{2}{c}{} \\
 & \textbf{Departament of Economics, Universidad de los Andes, Colombia.} \\
2019 - 2020 & Research Assistant at Centro de Estudios de Desarrollo Económico (CEDE) \\
            & Prof. Maria del Pilar López. \\
2018 - 2019 & Research Analyst at Centro de Estudios sobre Seguridad y Drogas (CESED). \\
            & Prof. Michael Weintraub. \\
\multicolumn{2}{c}{} \\
            & \textbf{Central Bank of Colombia.} \\
2016 - 2017 & Research Assistant at Centro de Estudios Económicos Regionales (CEER) \\
            & Researcher Leonardo Bonilla Mejía. \\
\multicolumn{2}{c}{} \\
            & \textbf{Departament of Economics, Universidad del Magdalena, Colombia.} \\
2015 - 2016 & Research Assistant at Grupo de Análisis en Ciencias Económicas (GACE) \\
            & Prof.  Etna Bayona. \\
\end{tabular}
\vspace{220pt}

%---- Teaching Experience ----%
\subsubsection*{Teaching Experience}
\vspace{-20pt}
\rule{\textwidth}{1pt} \hfill \\
\begin{tabular}{r|p{15cm}}
 & \textbf{Departament of Economics, Universidad de los Andes, Colombia.} \\
2019 - 2024 & Adjunct professor: Statistical \& R Programming  Workshop Seminar. \\
2021 - 2023 & Adjunct professor: Big Data and Machine Learning for Real Estate. \\
2021 - 2023 & Adjunct professor: Microsoft Excel Workshop Seminar. \\
2022 & Teaching Assitance: Big Data and Machine Learning for Applied Economics. \\
2019 - 2022 & Guest Lecturer: Module of Economics in Constitución y Democracia . \\
\multicolumn{2}{c}{} \\    
& \textbf{Departament of Economics and Bussines, Universidad del Magdalena, Colombia.} \\ 2021 & Adjunct professor: R Workshop for Applied Economics. \\
\multicolumn{2}{c}{} \\    
     & \textbf{Universidad Piloto de Colombia, Colombia.} \\
2021 &  Adjunct professor: Workshop at Geostatistics. \\
\end{tabular} 

%---- Conference Presentations ----%
\subsubsection*{Conference Presentations}
\vspace{-20pt}
\rule{\textwidth}{1pt} \\
Doctoral Workshop 2020-2022, VII Congreso de Economía Colombiana 2022 (UNU-WIDER), III National Colloquium of Doctoral Students in Economics 2020, Seminario CESED 2020, 2023.

%---- Fellowship and Awards ----%
\subsubsection*{Fellowship and Awards}
\vspace{-20pt}
\rule{\textwidth}{1pt} \\
\textbf{Departament of Economics, Universidad de los Andes:} Best paper of the doctoral workshop seminar (2022) and special mention (2021). \textbf{Ministerio de Ciencia y Tecnología de Colombia:} Economics Ph.D. Full Scholarship (2020-2022).

%---- Software ----%
%\subsubsection*{Computer Skills}
%\vspace{-20pt}
%\rule{\textwidth}{1pt}
%\textbf{Statistical software and computer language:} R, STATA, HTML, Python. \\
%\textbf{Applications:} QGIS, ARCGIS, LATEX, Git, Jupyter Notebook, Markdown.

%---- References ----%
\subsubsection*{References}
\vspace{-20pt}
\rule{\textwidth}{1pt}
\begin{multicols}{2}

\textbf{Rachid Laajaj} \\
Associate Professor \\
Departament of Economics \\ Universidad de los Andes \\
\href{mailto:r.laajaj@uniandes.edu.co}{r.laajaj@uniandes.edu.co} \\

\textbf{Leonardo Bonilla Mejía} \\
Researcher \\
Labor Economics Research Group \\ Central Bank of Colombia \\
\href{mailto:lbonilme@banrep.gov.co}{lbonilme@banrep.gov.co} \\

\textbf{Ignacio Sarmiento Barbieri} \\
Assistant Profesor \\
Departament of Economics \\ Universidad de los Andes \\
\href{mailto:i.sarmiento@uniandes.edu.co}{i.sarmiento@uniandes.edu.co} \\

\textbf{Michael Lee Weintraub} \\
Associate Professor \\
Escuela de Gobierno \\ Universidad de los Andes \\
\href{mailto:ml.weintraub@uniandes.edu.co}{ml.weintraub@uniandes.edu.co} \\
\end{multicols}
\end{document}
